Stock enhancement undermines community stability

### 2022-01-26 rmd/manuscript.Rmd
Update manuscript.Rmd

In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species $r_1$ (`r unique(sim_result$r1)`), mean strength of interspecific competition $\bar{\alpha}$ (`r unique(sim_result$alpha)`), carrying capacity $K$ (`r unique(sim_result$k)`), relative fitness of captive-bred individuals $f_R$ (`r unique(sim_result$phi)`), and degree of environmental stochasticity $\sigma_{\epsilon}$ (`r unique(sim_result$sd_env)`). We chose these parameters because our sensitivity analysis revealed that these parameters have the potential to alter the relationship between community dynamics and stock enhancement (**Supporting Information**). Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$). The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the number of species persist (defined as $N_i > 0.01$ at $t=1000$), the coefficient of variation (CV), the temporal mean, and the temporal SD. In addition, temporal means and SDs were calculated separately for the enhanced species $N_1$ and unenhanced species $\sum_{i,i \ne 1}^S N_i$ to infer mechanisms that underlie the community-level response.

@@

The only scenario where stock enhancement had little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**). In particular, stock enhancement increased the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**). This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021]. More importantly, the contrasting community response at different levels of carrying capacity provides deeper insights into ecosystem management. One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020]. However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats with compromised environmental capacity.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities. Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented. In protected watersheds where any form of exploitation is prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018]. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. In this study, we used the long-term data of stream fish communities (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**). The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])`. This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2**). In the meantime, the SDs had vague relationships with stock enhancement, and neither positive or negative relationship was supported by statistical analysis (**Figure 1B and 2**). At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010]. However, our analysis expands our understanding by illustrating the community-level response to stock enhancement in natural systems.

In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and previous observations confirm this assumption. Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018]. Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation). As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may impose resource competition that would otherwise not exist.

@@

Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations. However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships. Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables. Hence, we are confident in our statistical inference, and this unique study setup may have helped produce the close agreement between theory and empirical patterns.

@@

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations of enhanced species [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community. While our empirical example is limited to stream fish communities, the consistent emergence of destabilizing effect across simulated ecological scenarios implies that this ecological phenomenon is pervasive across terrestrial and aquatic taxa.

We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation. In particular, such efforts are crucial given that the undesired influence of stock enhancement is predicted to be exacerbated in degraded habitats due to the compromised capacity to support biodiversity (XX). It has been shown that protected areas and environmental restoration are promising tools to conserve biodiversity, and the effective spatial design is a key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017]. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that we have viable management options for the sustainable future of biodiversity and natural resources before blindly accepting stock enhancement programs. Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.

@@

In this study, we modified a multispecies Ricker model to include selective stock enhancement of a constituent species (species 1). In the basic model formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $\epsilon_{i,t} \sim Normal(0, \sigma_{\epsilon}^2)$. We modified this model formula to consider the effects of stock enhancement on reproduction and competition as follows:

@@

$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

@@

We varied values of the following ecological parameters: mean strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`), intrinsic growth of the enhanced species ($r_1 =$ `r unique(param_set$r1)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`). Other parameters were set constant or drawn randomly from a probability distribution: $S=$ `r unique(param_set$n_species)` , $K=$ `r unique(param_set$k)` , $r_i =$ $Unif$(`r unique(param_set$r_min)` , `r unique(param_set$r_max)`) ($i \ne 1$), $\alpha_{ii} = 1$, $\alpha_{ij,i \ne j} \sim Exp(\bar{\alpha})$. This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates). The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$. We initialized the community with populations of each species drawn from a poisson distribution with a mean of five. We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period). After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period). After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$). We also calculated temporal means and standard deviations for each species group. Values of simulation parameters were summarized in XXX. We performed simulations using R version XXX.

@@

$$
\begin{aligned}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state} &\text{(8)}
\end{aligned}
$$ where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$). This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites. We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).

We developed the following linear regression models taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.

$$
\begin{aligned}
\left\{
\begin{array}{}
ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&~\text{for CV, mean, and SD}\\
y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&\text{for species richness}
\end{array}
\right.
&\text{(9)}
\end{aligned}
$$

@@

$$
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &\text{(10)}
\end{aligned}
$$

@@

$$
\begin{aligned}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
&&\text{(11)}
\end{aligned}
$$

@@

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R. We assigned weakly informative priors for parameters, which were summarized in XXX. Data manipulation and analysis were performed in R version 4.1.0.

>>>>

In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`), and degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`). We chose these parameters because our sensitivity analysis revealed that these parameters were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**). Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$). The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean, and the temporal SD. In addition, temporal means and SDs were calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.

@@

The only scenario where stock enhancement had little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**). In particular, stock enhancement increased the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**). This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021]. More importantly, the contrasting community response at different levels of carrying capacity provides deeper insights into ecosystem management. One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020]. However, our results suggest that stock enhancement will not bring desired ecological outcomes in degraded habitats because human influences compromised environmental capacity.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities. Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented [@kitadaLessonsJapanMarine2020]. In protected watersheds where any forms of exploitation are prohibited (including recreational angling) (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018]. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criterion). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**). The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S7**). This pattern was associated with the reduced long-term average of total community density, and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Tables S7-S9** and **Figure 1B and 2**). In the meantime, the SDs had vague relationships with stock enhancement, and neither positive or negative relationship was supported by statistical analysis (**Figure 1B and 2**). At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010]. Our analysis builds upon these findings by illustrating the community-level response to stock enhancement in nature.

In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and previous observations confirm this assumption. Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018]. Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation). As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.

@@

Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations. However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships. Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S7-S9**). This unique study setup may have helped uncover the close agreement between theory and empirical patterns.

@@

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007a]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community. While our empirical example is limited to stream fish communities, the consistent emergence of destabilizing effect across simulated ecological scenarios implies that this ecological phenomenon is pervasive across terrestrial and aquatic taxa.

We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation. Such efforts are particularly important in the Anthropocene because the undesired influence of stock enhancement may be exacerbated in degraded habitats. Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017]. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that we have viable management options for the sustainable future of natural resources before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.

@@

We employed a multispecies Ricker model. In the basic formula without stock enhancement, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$. We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:

@@

$R_t$ is the number of released individuals, and the parameter $\phi_i$ controls the relative fitness of captive-bred individuals:

@@

In this model, the intrinsic growth rates for unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively. We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.

Prior to the main simulation analysis, we performed an extensive sensitivity analysis to identify parameters that strongly influence the relationship between community dynamics and stock enhancement. We identified five influential parameters, of which multiple values were considered in the main simulation as follows: carrying capacity ($K=$ `r unique(param_set$k)`), intrinsic growth of enhanced species ($r_1 =$ `r unique(param_set$r1)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(param_set$sd_env)`), relative fitness of captive-bred individuals ($f_R=$ `r unique(param_set$phi)`), and average strength of interspecific competition ($\bar{\alpha}=$ `r unique(param_set$alpha)`). We fixed values of the following parameters: the number of species ($S=$ `r unique(param_set$n_species)`) and the maximum intrinsic growth rate of unenhanced species ($r_{max}=$ `r unique(param_set$r_max)`). This simulation setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates). The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$. We initialized the community with populations of each species drawn from a poisson distribution with a mean of five. We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period). After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period). After the burn-in period, we continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps to obtain the coefficient of variation, temporal mean, and SD of whole community density ($\sum_i^SN_j$). Temporal means and SDs were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately. We summarized values of simulation parameters in **Table S1**.

@@

$$
\begin{aligned}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state} &\text{(8)}
\end{aligned}
$$ where $ln~r_{s}$ is the site-specific rate of change at site $s$ and $\epsilon_{s,t}^{state}$ is the process error that is assumed to follow a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$). This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites. We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$). Raw time series data and estimated community dynamics are shown in **Figures S12-S15**.

We developed the following linear regression model taking either CV, species richness, mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.

$$
\begin{aligned}
\left\{
\begin{array}{}
ln~y_s &\sim Normal(\mu_y, \sigma_y^2)~&&~\text{for CV, mean, and SD} &&&\text{(9a)}\\
y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s}))~&&\text{for species richness} &&&\text{(9b)}
\end{array}
\right.
\end{aligned}
$$

@@

$$
\begin{aligned}
\left\{
\begin{array}{}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD} &&&\text{(10a)}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness} &&&\text{(10b)}
\end{array}
\right.
\end{aligned}
$$

@@

$$
\begin{aligned}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)  &&\text{(11a)}\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w} &&\text{(11b)}
\end{aligned}
$$

@@

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package in R. We assigned weakly informative priors for parameters, which were summarized in **Table S6**. Data manipulation and analysis were performed in R version 4.1.0.
